%-------------------------
% Resume in Latex
% Author : Ömer Üstün
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}
 
\begin{center}
   
  {\Huge \scshape Muhammed Çelik} \\ \vspace{1pt}
    İnceyol St. No:35/6 Maltepe/İstanbul \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +90 530 153 5987 ~ \href{mailto:celikmuhammed@outlook.com.tr}{\raisebox{-0.2\height}\faEnvelope\  \underline{celikmuhammed@outlook.com.tr}} ~ 
    \href{https://www.linkedin.com/in/celikmuhammed/}{\raisebox{-0.2\height}\faLinkedin\ \underline{muhammedcelik}}  ~
    \href{https://github.com/muhammed-celik}{\raisebox{-0.2\height}\faGithub\ \underline{muhammed-celik}}
    \vspace{-8pt}
\end{center}


%-----------Professional Experience-----------
\section{Professional Experience}
    
    \resumeSubHeadingListStart
    \resumeSubheading
      {Procenne}{July 2022 -- August 2022}
      {Digital Design Intern}{İstanbul, TR}
        \resumeItemListStart
            \resumeItem{Worked on Secure Memory Project.}
            \resumeItem{Implemented AES ciphering algorithm in Verilog.}
            \resumeItem{Integrated AES design into SRAM Controller module to cipher plain-text data and store.}
            \resumeItem{Synthesized and implemented the top module design via OpenLane Flow.}
        \resumeItemListEnd

    \resumeSubheading
      {Pavelsis}{June 2022 -- July 2022}
      {Digital Design Intern}{İstanbul, TR}
        \resumeItemListStart
            \resumeItem{Worked on MAX1363 ADC IC Hardware Driver Project.}
            \resumeItem{Studied datasheet of MAX1363 to configure and operate properly.}
            \resumeItem{Developed I2C Controller in VHDL to communicate and transmit digital signals from the ADC to FPGA.}
            \resumeItem{Tested the design on the FPGA and verified correct functionality of the driver.}
        \resumeItemListEnd

    \resumeSubheading
      {Yongatek Microelectronics}{November 2021 -- June 2022}
      {Digital Design Intern}{İstanbul, TR}
        \resumeItemListStart
            \resumeItem{Worked on Turbo Encoder Project and translated the design into Verilog HDL.}
            \resumeItem{Utilized OpenLane Flow to generate GDSII file for Turbo Encoder Design.}
            \resumeItem{Worked on 5G New Radio LDPC Encoder project. Proposed a top level schematic and implemented the design in VHDL.}
            \resumeItem{Verified the LDPC Encoder design via VHDL testbench.}
        \resumeItemListEnd
          
          
    \resumeSubHeadingListEnd
  \vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bogazici University}{September 2018 -- }
      {Senior Electrical and Electronics Engineering student}{İstanbul, TR}
        \resumeItemListStart
            \resumeItem{Current GPA: 3.19/4.00}
            \resumeItem{Member, BUEC IEEE Student Branch (2019-2020)}
            \resumeItem{Member, UAV-IN Unmanned Aerial Vehicle Team (2019-2020)}
            \resumeItem{MSMB, Mimar Sinan Engineering Society}
        \resumeItemListEnd
    %\resumeSubheading
    %  {Private Asfa High School}{September 2014 -- June 2018}
    %  {Science Class}{İstanbul, TR}
    %  \resumeItemListStart
    %    \resumeItem{Graduate GPA: 98/100}
    %    \resumeItem{Member, Robotics Student Club}
    %\resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{UART Transmitter \& Receiver Module} $|$ \emph{VHDL, Xilinx Vivado, XSim}}{September 2021}
          \resumeItemListStart
            \resumeItem{The project involves digital design of both transmitter and receiver components of UART communication protocol.}
            \resumeItem{The data to be transmitted is set as 1 byte.}
            \resumeItem{Clock frequency, baudrate and stop bit number are set as generic to implement the modules for various setups.}
            \resumeItem{The design is verified by Vivado testbench simulations.}
          \resumeItemListEnd
          
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Prime Number Detector} $|$ \emph{VHDL, Xilinx ISE, ISim}}{June 2021}
          \resumeItemListStart
            \resumeItem{Digital Systems Design project aims to find first 256 prime numbers and display them on a VGA monitor consecutively.}
            \resumeItem{In order to detect prime numbers among the other integers, Sieve of Eratosthenes algorithm is used with sufficient number of prime counters.}
            \resumeItem{After detection of the primes, numbers are converted into BCD format to be displayed on the screen.}
            \resumeItem{Using VGA interface of Xilinx Spartan FPGA, prime numbers are printed on the screen one by one.}
          \resumeItemListEnd 
          
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Computing Eigenvalues and Eigenvectors} $|$ \emph{C++}}{April 2021}
          \resumeItemListStart
            \resumeItem{Aim of the project is implementing the normalized power iteration algorithm together with deflation to find two eigenvalues and corresponding eigenvector for the dominant eigenvalue of a given matrix A, where A is a square matrix.}
            \resumeItem{The program takes three command line arguments for the parameters: Name of the file which includes matrix A, tolerance and name of the output file.}
            \resumeItem{To implement Object Oriented Programming, matrix class is defined. Entries of matrices are stored in dynamic 2-d vector variable.}
            \resumeItem{Matrix operations such as addition, multiplication, transpose are defined as class methods.}
          \resumeItemListEnd 


    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Turkish (Native), English (Advanced)} \\
     \textbf{Programming}{: C/C++, Python, VHDL, Verilog HDL, MATLAB} \\
     \textbf{Technology/Tools}{: GNU/Linux, Microsoft Office, Xilinx Vivado/ISE, QuestaSim, Caravel OpenLane, LTSpice, Simulink} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------BASARILAR---------------



\end{document}